### 2012-02-23 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\subsection{Auxiliary Functions}
\todo[inline]{Dalsie pomocne funkcie a okomentovat.}
\todo[inline]{Algoritmu pouzivaju nejake nedefinovane funkcie, napr stepNode.getAxisNode().}

@@

@@

@@

@@

\FORALL{$bindingNode \in bindingNodes$}
    \STATE $bindingExpr = bindingNode.getChild(BindingSequenceNode).$ $getChild(ExprNode)$
    \IF{$getType(BindingExpr) == PathType$ using only child and descendant axes, ending with exactly one predicate $P$}
        \FORALL{$(var, node) \in forVars$}
            \STATE $forVars = determinateJoinPatterns(bindingNode, P, node, var,$ $forVars,$ $checkJoinPattern3,$ $whereExpr)$
        \ENDFOR
    \ELSIF{$getType(BindingExpr) == PathType$ without predicates using only child and descendant axes}
        \IF{$is(bindingNode, ForClauseNode$}
            \STATE add $(bindingNode.varName, bindingNode)$ to forVars
        \ENDIF
    \ENDIF
\ENDFOR

@@

\FORALL{$jpOccurrence \in \mathcal{O}$}
    \IF{$jpOccurrence$ is the for join pattern}
        \STATE mark $jpOccurrence$ as case (O1), weight 1
    \ELSIF{$jpOccurrence$ is the join pattern 3}
        \STATE mark $jpOccurrence$ as case (O1), weight 0.5
    \ELSE
        \STATE TODO (R2,R3,R4,R5)
    \ENDIF
    \STATE update $jpOccurrence$ in $\mathcal{O}$
\ENDFOR

>>>>

\subsection{Auxiliary Functions}
Firstly, we define some auxiliary functions used by algorithms in this chapter.

Function $usesOnlyChildAndDescendantAxes$ in Algorithm \ref{ALG_function_uses_only_child_and_descendant_axes} takes an instance of $PathType$ as its arguments and returns true if the path uses only child and descendant axes. Otherwise, it returns false.

@@

Function $isWithoutPredicates$ in Algorithm \ref{ALG_function_is_without_predicates} checks whether a path represented by a given $PathType$ instance does not contain predicates. A Similar function is  $isWithoutPredicatesExceptLastStep$. This function is not explicitly defined, because its definition is the same as the definition of function $isWithoutPredicates$, except it does not check the last step of the path. So the last step may contain predicates and the function will return true.

@@

Function $endsWithExactlyOnePredicate$ checks if a path represented by a given $PathType$ instance contains exactly one predicate in its last step and if so, the predicate is returned. Otherwise, it returns false.

@@

\todo[inline]{Algoritmy pouzivaju nejake nedefinovane funkcie, napr stepNode.getAxisNode().}

@@

\FORALL{$bindingNode \in bindingNodes$}
    \STATE $bindingExpr = bindingNode.getChild(BindingSequenceNode).$ $getChild(ExprNode)$
    \STATE $type = getType(bindingExpr)$
    \IF{$type$ is $PathType$ $AND$ $usesOnlyChildAndDescendantAxes(type)$ $AND$ $isWithoutPredicatesExceptLastStep(type)$}
    	\STATE $P = endsWithExactlyOnePredicate(type)$
    	\IF{$P$}
        	\FORALL{$(var, node) \in forVars$}
            	\STATE $forVars = determinateJoinPatterns(bindingNode, P, node, var,$ $forVars,$ $checkJoinPattern3,$ $whereExpr)$
        	\ENDFOR
        \ELSIF{$isWithoutPredicates(type)$}
        	\IF{$is(bindingNode, ForClauseNode$}
            	\STATE add $(bindingNode.varName, bindingNode)$ to forVars
        	\ENDIF
        \ENDIF
    \ENDIF
\ENDFOR

@@

\todo[inline]{Definovat getParent() na Node.}
\todo[inline]{Popisat preco raz bereme target return path types a raz priamo paths.}

\FORALL{$jpOccurrence \in \mathcal{O}$}
    \IF{$jpOccurrence$ is the for join pattern}
        \STATE mark $jpOccurrence$ as case (O1), weight 1
    \ELSIF{$jpOccurrence$ is the join pattern 3}
        \STATE mark $jpOccurrence$ as case (O1), weight 0.5
    \ELSE
        \STATE $secondBindingNode =$ the second binding node from $jpOccurrence$
        \STATE $flworNode = secondBindingNode.getParent().getParent()$
        \STATE $secondVarName = secondBindingNode.varName$
        \STATE $returnPathTypes = getReturnPathTypes(flworNode, secondVarName)$
        \FORALL{$returnPathType \in returnPathTypes$}
        	\IF{$returnPathType.specialFunctionCalls$ contains one of $min$, $max$, $sum$, $avg$}
        		\STATE mark $jpOccurrence$ as case (O1), weight 1 // R2
        		\STATE continue the outmost for cycle with next $jpOccurrence$
        	\ENDIF
        \ENDFOR
        \FORALL{$returnPathType \in returnPathTypes$}
        	\IF{$returnPathType.specialFunctionCalls$ contains $count$}
        		\STATE mark $jpOccurrence$ as case (O1), weight 0.75 // R3
        		\STATE continue the outmost for cycle with next $jpOccurrence$
        	\ENDIF
        \ENDFOR
        \STATE $targetReturnPaths = getTargetReturnPaths(flworNode, secontVarName)$
        \STATE $retPathsNumber = $ number of paths in $targetReturnPaths$
        \IF{$retPathsNumber > 1$}
        	\STATE mark $jpOccurrence$ as case (O2), weight 1 // R4
        \ELSE
            \STATE mark $jpOccurrence$ as case (O2), weight 0.5 // R5
        \ENDIF
    \ENDIF
    \STATE update $jpOccurrence$ in $\mathcal{O}$
\ENDFOR
